GeneSet_Expansion

### 2020-05-16 code/Jansen_SMR.Rmd
Jansen SMR

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
activityName = 'Mendelian Randomization';
activityDescription = 'Validation of TWAS associations via SMR analysis';
CODE <- syn_temp$store(synapseclient$Folder(name = "Summary-data-based Mendelian Randomization", parentId = parentId))
# Set annotations
all.annotations = list(
  dataType = 'analysis',
  dataSubType = 'SMR_Validation_Tests',
  summaryLevel = 'gene',
  assay	 = 'TWAS',
  tissueTypeAbrv	= c('NA'), 
  study = c('ROSMAP','MSBB', 'Mayo'),
  organism = 'HomoSapiens',
  consortium	=  c('ROSMAP','MSBB', 'Mayo') ,
  normalizationStatus	= TRUE,
  normalizationType	= 'NA',
  rnaquantification = 'NA',
  genomeAssemblyID = 'hg19'
)
# Store SMR
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='Final_SMR_TWAS_Jansen_Validation.tsv', name = 'SMR Values', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'Summary Stats'
syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
```

>>>>

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
activityName = 'Mendelian Randomization';
activityDescription = 'Validation of TWAS associations via SMR analysis';
CODE <- syn_temp$store(synapseclient$Folder(name = "Jansen_SMR", parentId = parentId))
# Set annotations
all.annotations = list(
  dataType = 'analysis',
  dataSubType = 'SMR_Validation_Tests',
  summaryLevel = 'gene',
  assay	 = 'TWAS',
  tissueTypeAbrv	= c('NA'), 
  study = c('ROSMAP','MSBB', 'Mayo'),
  organism = 'HomoSapiens',
  consortium	=  c('ROSMAP','MSBB', 'Mayo') ,
  normalizationStatus	= TRUE,
  normalizationType	= 'NA',
  rnaquantification = 'NA',
  genomeAssemblyID = 'hg19'
)
# Store SMR
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='Final_SMR_TWAS_Jansen_Validation.tsv', name = 'SMR Values', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'Summary Stats'
syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
```
